Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-05-14 ltx/data_paper/DataPaper.tex
edit to plot captions
changed the title

\title{Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data}
\author{In no specific order: Parham Aram, Dean R. Freestone, Kenneth Scerri, Michael Dewar,\\
 Andrew Zammit Mangion, Jacob A. Donoghue, Sydney S. Cash, Leigh R. Hochberg,\\
 David B. Grayden and Visakan Kadirkamanathan  }

@@

The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
\begin{align}
	\mathbf W_0^{(m)}&=\frac{\lambda}{ n_x+\lambda} \\
	\mathbf W_0^{(c)}&=\frac{\lambda}{ n_x+\lambda}+(1-\alpha^2+\beta) \\
	\mathbf W_i^{(m)}&=\mathbf W_i^{(c)}=\frac{1}{2( n_x+\lambda)} \quad i=1, \dots, 2n_x, 
\end{align}
where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ (for a Gaussian disturbance, $\beta$ should be set to 2 \cite{Haykin2001}). Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states. The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above. The predicted and the smoothed cross-covariance matrices of the states, $\mathbf M_{t}^{b-}$ and  $\mathbf M_{t}^{b}$, are also required. The former is used  for computing the smoother gain and the latter is used to compute expected log-likelihood. The formulation of the cross-covariance matrices are given in the summary of the steps in the URTSS algorithm in Table~\ref{tab:URTSSAlgorithm}.

@@

It is well known that the expected joint data log likelihood $\ln p(\mathbf X,\mathbf Y;\boldsymbol\Theta)$, forms a lower bound on the log-likelihood function $\ln p(\mathbf Y;\boldsymbol\Theta)$, where $\mathbf X$ and $\mathbf Y$ are set of all states and the set of all observations respectively and $\boldsymbol \Theta$ denotes the set of all system parameters. Therefore we can write

@@

\dean{Dean to check expansion.} Now we rearrange the equation so we can  use the information from the smoother. (or isolate (reason for doing this step is..)) the cross-covariance etc. Taking trace and rearranging, using the invariant cyclic permutations property of the trace, thess distributions can be written as

@@

Covariance and cross-covariances in equation \eqref{eq:VoldermontwitXivariables}, consist of both linear terms, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$. Finding linear $\boldsymbol\Xi$-variables is straightforward as they can be computed directly using smoother outputs, i.e. $\hat{\mathbf x}_t^b $, $\mathbf P_t^b$ and $\mathbf M_t^b$ using the following expressions \cite{Gibsona2005} (see supporting information for details)

@@

However calculation of non-linear $\boldsymbol\Xi$-variables is not straightforward as in the linear case. Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is to be used in the calculations of the $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$. This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the smoothed state, $\hat{\mathbf x}_t^b$ at each time instant, i.e.

@@

Having approximated $q\left(\mathbf x_t\right)$, by substituting  \eqref{eq:qTaylor} into equations (\ref{eq:Xi3}-\ref{eq:Xi5}) an approximate to the non-linear $\boldsymbol\Xi$-variables can be calculated which in turn provides an approximate lower bound on the log-likelihood function (see supporting information), 
\begin{align}
\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\	
\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t\right] \\
 \boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] 
 \end{align}
where
\begin{align}\label{eq:lambdat} 
	{\boldsymbol \lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'
\end{align}
and
\begin{equation}
 \boldsymbol\Lambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P_t}]_{ij}{\boldsymbol\lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\lambda}_t^{(j)}
\end{equation}

Given the state estimates, $\mathbf {\hat x}_t$ the state covariance $\mathbf P_t$ and cross-covariance $\mathbf M_t$ , the $\boldsymbol\Xi$-variables can be computed directly.  The computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}. In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found in \cite{Sarkka2010}.

@@

We comment on the condition under which $\boldsymbol\Xi_4$ is invertible later on. The second derivative is negative definite at this stationary point, and hence it is a global maximizer of $\mathcal{Q}$-function. Now maximizing with respect to $\sigma_{\epsilon}^2$ we get

@@

A second derivative test shows that this is indeed the maximum. Finally differentiating with respec to $\sigma_d^2$ we get

@@

setting above to zero and solving for $\sigma_e^2$ we have

@@

	\boldsymbol\Theta = \left\lbrace \boldsymbol\theta, \xi, \sigma^2_d, \sigma^2_{\epsilon}\right\rbrace 
\end{equation} We choose to maximise \dean{the joint}, $p(\mathbf X,\mathbf Y;\boldsymbol \Theta)$, since it is not  possible to maximise the likelihood function $p(\mathbf Y;\boldsymbol\Theta)$ directly. Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}. 

@@

\section{Results}
This section demonstrates the identification of the proposed IDE model using simulated data. The observation noise and disturbance were unknown to the estimation algorithm and no assumption were made on the shape of the kernel.  Data was generated employing state space equation (\ref{eq:StateEq}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$, assuming the observed field can be fully described by the decomposed IDE model. 100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach steady state. The observation noise was set to $\Sigma_{\epsilon}=0.2\times \mathbf I_{n_y}$ and the field disturbance was set to $\mathcal{GP}(\mathbf 0,0.1 \times\gamma(\mathbf{r}-\mathbf{r}'))$ where the covariance function was chosen as a Gaussian with zero mean and the width $\sigma_{\gamma}^2=1.7~mm^2$ . The distance between adjacent sensors was 1.5 mm resulting into $n_y = 196$ observations. The width of the sensor kernels were set to $\sigma_m^2=0.81~mm^2$. The sampling period and the synaptic time constant were set to $T_s = 1~ms$  and $\tau = 10~ms$, respectively. The sigmoidal activation parameters were $\varsigma=0.56~mV^{-1}$ and $v_0=1.8~mV$.

@@

\begin{itemize}
	\item comment on how the e step is UKF and M-step is kinda like the EKF, and we dont use EKF in E-step since UKF gives better estimates and the linearisation in M-step would be more accurate. 
	\item comment on EM has been used with EKS by Ghahramani which has poorer convergance property (I guess) using EM with URTSS
	\item itterative EM and correlation analysis (maybe)
	\item{comment on EM might convrge to suboptimal solution,simulated
annealing can be used to tackle such situations but difficult to implement (Mc Lachlan)}
\end{itemize}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelBasis1.pdf}
\end{center}
\caption{{\bf Connectivity kernel support approximation.} The approximate support of the kernel is shown by the red circle. Black area shows the non-zero values of the support after thresholding. A $5\times5$ grid of basis functions (blue circles) used to reconstruct the connectivity kernel.}
\label{fig:KernelWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
\end{center}
\caption{{\bf Disturbance support approximation}. }
\label{fig:DisturbanceWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimate.pdf}
\end{center}
\caption{{\bf Connectivity kernel estimates.} (A) Actual kernel. (B) The mean kernel estimate over 100 realisations}
\label{fig:KernelEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
\end{center}
\caption{{\bf Cross-sections of connectivity kernel estimates.} Actual kernel and the mean kernel estimates are shown with blue and green lines respectively. Each of the estimate from Monte Carlo simulation is shown with black line. The 95\% confidence intervals are shown by shaded red area.}
\label{fig:KernelEstimateCrossSection}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Histogram.pdf}
\end{center}
\caption{{\bf Histograms of the parameter estimates over 100 realizations}. The actual and mean of the estimated parameter values are shown by solid and dotted lines respectively. (A) The histogram of the synaptic dynamic parameter, $\xi$. (B) The histogram of the observation noise variance, $\sigma_{\epsilon}$. (C) The histogram of the disturbance noise variance, $\sigma_d^2$}.
\label{fig:Histogram}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics[scale=1]{./Figures/FieldEstimates.pdf}
\end{center}
\caption{{\bf Field Estimates}. }
\label{fig:FieldEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Q.pdf}
\end{center}
\caption{{\bf Lower-bound of the log-likelihood}. $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$.}
\label{fig:LowerBound}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

>>>>

\title{Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm}
\author{In no specific order: Parham Aram, Dean R. Freestone, Kenneth Scerri, Michael Dewar,\\
 Andrew Zammit Mangion, Jacob A. Donoghue, Sydney S. Cash, Leigh R. Hochberg,\\
 David B. Grayden and Visakan Kadirkamanathan  }

@@

The sigma vectors are propagated through the system equations and weighted to form the predicted mean and covariance. The weights are calculated by 
\begin{align}
	\mathbf W_0^{(m)}&=\frac{\lambda}{ n_x+\lambda} \\
	\mathbf W_0^{(c)}&=\frac{\lambda}{ n_x+\lambda}+(1-\alpha^2+\beta) \\
	\mathbf W_i^{(m)}&=\mathbf W_i^{(c)}=\frac{1}{2( n_x+\lambda)} \quad i=1, \dots, 2n_x, 
\end{align}
where the superscripts $m$ and $c$ denote mean and covariance and $\beta$ incorporates prior knowledge of the distribution of the states, $\mathbf{x}$ (for a Gaussian disturbance, $\beta$ should be set to 2 \cite{Haykin2001}). Since the observation equation is linear (equation~\ref{ObservationEquation}), the standard Kalman Filter update equations are used to correct the predicted states. The state estimates from forward filtering are used to form a new set of sigma points for the smoother, as described above. The predicted and the smoothed cross-covariance matrices of the states, $\mathbf M_{t}^{b-}$ and  $\mathbf M_{t}^{b}$, are also required. The former is used  for computing the smoother gain and the latter is used to compute expected log-likelihood function. The formulation of the cross-covariance matrices are given in the summary of the steps in the URTSS algorithm in Table~\ref{tab:URTSSAlgorithm}.

@@

It is well known that the expected joint data log likelihood $\ln p(\mathbf X,\mathbf Y;\boldsymbol\Theta)$, forms a lower bound on the log-likelihood function $\ln p(\mathbf Y;\boldsymbol\Theta)$, where $\mathbf X$ and $\mathbf Y$ are set of all states and the set of all observations respectively and $\boldsymbol \Theta$ denotes the set of all system parameters, i.e.
	\boldsymbol\Theta = \left\lbrace \boldsymbol\theta, \xi, \sigma_d, \sigma_{\epsilon}\right\rbrace 
 Therefore we can write

@@

\dean{Dean to check expansion.} Now we rearrange the equation so we can  use the information from the smoother. (or isolate (reason for doing this step is..)) the cross-covariance etc. Taking trace and rearranging, using the invariant cyclic permutations property of the trace, equations \eqref{eq:CondititionDist1} and \eqref{eq:CondititionDist2} become

@@

Covariance and cross-covariances in equation \eqref{eq:VoldermontwitXivariables}, consist of both linear terms, $\boldsymbol\Xi_0$, $\boldsymbol\Xi_1$ and $\boldsymbol\Xi_2$ and non-linear terms, $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and  $\boldsymbol\Xi_5$. Finding linear $\boldsymbol\Xi$-variables is straightforward as they can be computed directly using smoother outputs, i.e. $\hat{\mathbf x}_t^b $, $\mathbf P_t^b$ and $\mathbf M_t^b$ using following expressions \cite{Gibsona2005} (see supporting information for details)

@@

However calculation of non-linear $\boldsymbol\Xi$-variables is not straightforward as in linear case. Therefore, an additional  Taylor expansion step to the URTSS algorithm is also created to approximate $q(\mathbf{x}_t)$ at each time instant which is to be used in  calculations of $\boldsymbol\Xi_3$, $\boldsymbol\Xi_4$ and $\boldsymbol\Xi_5$. This is accomplished by taking the first-order truncated Taylor-series expansion of the sigmoidal activation function  around the smoothed state, $\hat{\mathbf x}_t^b$ at each time instant, i.e.

@@

Having approximated $q\left(\mathbf x_t\right)$, by substituting  \eqref{eq:qTaylor} into equations (\ref{eq:Xi3}-\ref{eq:Xi5}) an approximate to the non-linear $\boldsymbol\Xi$-variables can be calculated (see supporting information) which in turn provides an approximate lower bound on the log-likelihood function, 
\boldsymbol\Xi_{3}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t+1}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf M_{t+1} \tilde{\boldsymbol\Sigma}_e^{-1} \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] \\	
\boldsymbol\Xi_{4}&\approx\sum_{t=0}^{T-1}\left[q^\top(\mathbf{\hat x}_t)\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\Lambda_t\right] \\
 \boldsymbol\Xi_{5}&\approx\sum_{t=0}^{T-1}\left[ \mathbf{\hat x}_{t}^\top\tilde{\boldsymbol\Sigma}_e^{-1}q(\mathbf{\hat x}_t)+\int_\Omega\boldsymbol \phi^\top(\mathbf r') \mathbf P_t \tilde{\boldsymbol\Sigma}_e^{-1}  \boldsymbol{\Psi}(\mathbf{r}') f'(\boldsymbol \phi^\top(\mathbf r')\mathbf {\hat x}_t) d\mathbf{r}'\right] 
\begin{align}\label{eq:lambdat} 
	{\boldsymbol \lambda}_t^{(i)}&=\int_{\Omega} \boldsymbol \Psi(\mathbf r')\phi_i(\mathbf r')f'(\boldsymbol\phi^\top(\mathbf r')\mathbf {\hat x}_t)d\mathbf r'
and
 \boldsymbol\Lambda_t=\sum_{i,j=1}^{n_x}[\mathbf{P_t}]_{ij}{\boldsymbol\lambda}_t^{(i)\top}\tilde{\boldsymbol\Sigma}_e^{-1}{\boldsymbol\lambda}_t^{(j)}
By computing $\boldsymbol\Xi$-variables, calculation of the lower bound is complete. The lower bound now can be used in M-step to find a set of new parameters. The computational complexity of the algorithm is given in Table~\ref{table:ComputationalComplexity}. In this table only the computational complexity of variables specific to the presented algorithm are shown, and the computational complexity of the URTSS can be found elsewhere \cite{Sarkka2010}.

@@

We comment on the condition under which $\boldsymbol\Xi_4$ is invertible later on. Now maximizing with respect to $\sigma_{\epsilon}^2$ we get

@@

Finally differentiating with respec to $\sigma_d^2$ we get

@@

setting above to zero and solving for $\sigma_d^2$ we have

@@

%  Increasing the joint likelihood function increases the likelihood function $p(\mathbf Y;\boldsymbol \Theta)$ \cite{McLachlan1997}. 

@@

\section{Results}
This section demonstrates the identification of the proposed IDE model using simulated data. The observation noise and disturbance were unknown to the estimation algorithm and no assumption were made on the shape of the kernel.  Data was generated employing state space equation (\ref{eq:StateEq}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$, assuming the observed field can be fully described by the decomposed IDE model. 100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach steady state. The observation noise was set to $\Sigma_{\epsilon}=0.2\times \mathbf I_{n_y}$ and the field disturbance was set to $\mathcal{GP}(\mathbf 0,0.1 \times\gamma(\mathbf{r}-\mathbf{r}'))$ where the covariance function was chosen as a Gaussian with zero mean and the width $\sigma_{\gamma}^2=1.7~mm^2$ . The distance between adjacent sensors was 1.5 mm resulting into $n_y = 196$ observations. The width of the sensor kernels were set to $\sigma_m^2=0.81~mm^2$. The sampling period and the synaptic time constant were set to $T_s = 1~ms$  and $\tau = 10~ms$, respectively. The sigmoidal activation parameters were $\varsigma=0.56~mV^{-1}$ and $v_0=1.8~mV$.

@@

\begin{itemize}
	\item comment on how the e step is UKF and M-step is kinda like the EKF, and we dont use EKF in E-step since UKF gives better estimates and the linearisation in M-step would be more accurate. 
	\item comment on EM has been used with EKS by Ghahramani which has poorer convergance property than using EM with URTSS
	\item itterative EM and correlation analysis (maybe)
	\item{comment on EM might convrge to suboptimal solution,simulated
annealing can be used to tackle such situations but difficult to implement (Mc Lachlan)}
	\item{since the non-linearity is a sigmoid function first-order Taylor provide a good approximation however in general settings with more complicated nonlinear behaviours higher order terms might need to be included, this however introduce intractable computational complexity.}
\end{itemize}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelBasis1.pdf}
\end{center}
\caption{{\bf Connectivity kernel support approximation.} The approximate support of the kernel is shown by the red circle. Black area shows the non-zero values of the support after thresholding. A $5\times5$ grid of basis functions (blue circles) used to reconstruct the connectivity kernel.}
\label{fig:KernelWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
\end{center}
\caption{{\bf Disturbance support approximation}. }
\label{fig:DisturbanceWidthEstimation}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimate.pdf}
\end{center}
\caption{{\bf Connectivity kernel estimates.} (A) Actual kernel. (B) The mean kernel estimate over 100 realisations}
\label{fig:KernelEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelEstimateCrossSection.pdf}
\end{center}
\caption{{\bf Cross-sections of connectivity kernel estimates.} Actual kernel and the mean kernel estimates are shown with blue and green lines respectively. Each of the estimate from Monte Carlo simulation is shown with black line. The 95\% confidence intervals are shown by shaded red area.}
\label{fig:KernelEstimateCrossSection}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Histogram.pdf}
\end{center}
\caption{{\bf Histograms of the parameter estimates over 100 realizations}. The actual and mean of the estimated parameter values are shown by solid and dotted lines respectively. (A) The histogram of the synaptic dynamic parameter, $\xi$. (B) The histogram of the observation noise variance, $\sigma_{\epsilon}$. (C) The histogram of the disturbance noise variance, $\sigma_d^2$}.
\label{fig:Histogram}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics[scale=1]{./Figures/FieldEstimates.pdf}
\end{center}
\caption{{\bf Neural field estimates at different time instants}. In each subplot, true (gray line) and reconstructed neural field (red dots) are plotted versus spatial index.}
\label{fig:FieldEstimates}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/Q.pdf}
\end{center}
\caption{{\bf Lower-bound of the log-likelihood}. $Q(\boldsymbol\Theta',\boldsymbol\Theta')=-(T-1)\left[n_y(1+\ln \hat{\sigma}^2_{\epsilon})+ n_x(1+\ln \hat{\sigma}^2_d)\right]$.}
\label{fig:LowerBound}
\end{figure}
%~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
